\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex} \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}

### 2018-02-14 Draft_Form/tex/Materials_and_Methods(2).tex
update 14_02_2018
update 14_02_2018

The German National Forest Inventory (German NFI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The most recent inventory (BWI3) was conducted in the years 2011 and 2012. While information was originally gathered at a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres (Picture). The number of plots per cluster can however vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the tree-individual inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a diameter at breast height ($dbh$) of at least 7 cm. For each sample tree that is selected by this procedure, the dbh, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to calculate a volume estimation on the tree level. These volume estimations are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

@@

The tree species map information was used to predict the main tree species of the sample trees at each sample plot (\textit{treespecies}) as an additional categorical variable. This implied two consecutive processing steps. In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the edge-corrected support were classified as that species. Otherwise, the sample location was assigned the value 'mixed'. Likewise for the CHM variables, the support radius was 12 meters although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in section \ref{sec:SAestimators}. When using the \textit{treespecies} variable in a regression model, the support size and the percentage threshold particularly constitute parameters to be optimized in order to achieve an optimal variance decomposition of the data that subsequently leads to the best possible model accuracy. A detailed analysis and description of the optimal processing parameters for the explanatory variables of the present data set is provided in \citet{hill2017a}. In this study, the authors also applied a calibration model to the initially derived \textit{treespecies} variable that successfully removed the effects of misclassification errors on the regression model coefficients and increased the model accuracy. The calibration model consists of a decision tree from a random forest algorithm \citet{breiman2001} that was trained to predict the actual main plot tree species (known for all terrestrial plots) based on available auxiliary variables. These variables were the predicted \textit{treespecies} variable, the mean canopy height and standard deviation of the CHM, as well as the proportion of coniferous trees estimated from the classification map and the growing region derived from a polygon map. The algorithm was grown with 2000 trees considering $\sqrt{p} \approx$ 3 of the predictors for each split. In a \textit{second} step, we thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$. Table \ref{tab:classacc} gives the classification accuracies of the \textit{treespecies} variable before and after calibration.

>>>>

The German National Forest Inventory (German NFI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The most recent inventory (BWI3) was conducted in the years 2011 and 2012. While information was originally gathered at a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of maximal four sample locations (also referred to as \textit{sample plots}) that are arranged in a square (so called \textit{cluster}) with a side length of 150 metres. The number of plots per cluster can however vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the tree-individual inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a diameter at breast height ($dbh$) of at least 7 cm. For each sample tree that is selected by this procedure, the dbh, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to calculate a volume estimation on the tree level. These volume estimations are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

@@

The tree species map information was used to predict the main tree species of the sample trees at each sample plot (\textit{treespecies}) as an additional categorical variable. This implied two consecutive processing steps. In the \textit{first} step, one of the five tree species was assigned to a sample location if 100\% of the raster values within the edge-corrected support were classified as that species. Otherwise, the sample location was assigned the value 'mixed'. Likewise for the CHM variables, the support radius was 12 meters although the use of different support sizes for each explanatory variable would be in agreement with the two-phase estimators presented in section \ref{sec:SAestimators}. When using the \textit{treespecies} variable in a regression model, the support size and the percentage threshold particularly constitute parameters to be optimized in order to achieve an optimal variance decomposition of the data that subsequently leads to the best possible model accuracy. A detailed analysis and description of the optimal processing parameters for the explanatory variables of the present data set is provided in \citet{hill2017a}. In this study, the authors also applied a calibration model to the initially derived \textit{treespecies} variable that successfully removed the effects of misclassification errors on the regression model coefficients and increased the model accuracy. The calibration model consists of a decision tree from a random forest algorithm \citet{breiman2001} that was trained to predict the actual main plot tree species (known for all terrestrial plots) based on available auxiliary variables. These variables were the predicted \textit{treespecies} variable, the mean canopy height and standard deviation of the CHM, as well as the proportion of coniferous trees estimated from the classification map and the growing region derived from a polygon map. The algorithm was grown with 2000 trees considering $\sqrt{p} \approx$ 3 of the predictors for each split. In a \textit{second} step, we thus applied this calibration model to the \textit{treespecies} variable derived at all sample locations $s_1$. Table \ref{tab:classacc} gives the classification accuracies of the \textit{treespecies} variable after calibration.
